Prediction of Early Periprosthetic Joint Infection after Total Hip Arthroplasty

### 2022-01-28 reports/article.Rmd
manual changes made to Word files before submission

We used R version 4.1 (R Foundation for Statistical Computing, Vienna, Austria) with significant packages coder,[@Bulow2020b] decoder, furrr, pROC, rms, tidymodels and tidyverse. We build a shiny-based web calculator to aid clinical usage (https://erikbulow.shinyapps.io/thamortpred/) and made all R scripts publicly available (XXXXXXXXXXXXX).

>>>>

We used R version 4.1 (R Foundation for Statistical Computing, Vienna, Austria) with significant packages coder,[@Bulow2020b] decoder, furrr, pROC, rms, tidymodels and tidyverse. We build a shiny-based web calculator to aid clinical usage (https://erikbulow.shinyapps.io/thamortpred/) and made all R scripts publicly available (https://doi.org/10.5281/zenodo.5914599).
